%
%Academic CV LaTeX Template
% Author: Radwan Abdullah Al-Shawesh
% License: MIT
%
% For errors, suggestions, or improvements, please contact:
%

\documentclass[a4paper,11pt]{article}

% Custom Packages
\usepackage{CJKutf8}
\usepackage[table,xcdraw]{xcolor}

% Biblatex
\usepackage[style=ieee, defernumbers=true, backend=biber]{biblatex}
\addbibresource{bibliography.bib}

% Template Package imports
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}
\usepackage{multirow}
\usepackage{comment}
%\usepackage{cfr-lm}


% Color definitions
\definecolor{darkblue}{RGB}{0,0,139}

% Page layout
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\setlength{\footskip}{5pt} % Addressing fancyhdr warning

% Hyperlink setup (moved after fancyhdr to address warning)
\usepackage[hidelinks]{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=darkblue,
	filecolor=darkblue,
	urlcolor=black,
}

% Custom box settings
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={},
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

% URL style
\urlstyle{same}

% Text alignment
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
	\item{
		\textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
	}
}

\newcommand{\resumePOR}[3]{
	\vspace{0.5mm}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
	\end{tabular*}
	\vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{0.5mm}\item
	\begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textit{\footnotesize{#4}} \\
		\textit{\footnotesize{#3}} &  \footnotesize{#2}\\
	\end{tabular*}
	\vspace{-1.0mm}
}

\newcommand{\resumeProject}[4]{
	\vspace{0.5mm}\item
	\begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textit{\footnotesize{#3}} \\
		\footnotesize{\textit{#2}} & \footnotesize{#4}
	\end{tabular*}
	\vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\circ$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm]}
	\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
		\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,itemsep=0.5mm]}
			
			\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
		\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
	\vspace{2mm}
	\begin{tcolorbox}
		\textbf{\large #1}
	\end{tcolorbox}
	\vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

% Commands for icon sizing and positioning
\newcommand{\socialicon}[1]{\raisebox{-0.05em}{\resizebox{!}{1em}{#1}}}
\newcommand{\ieeeicon}[1]{\raisebox{-0.3em}{\resizebox{!}{1.3em}{#1}}}

% Font options
\newcommand{\headerfonti}{\fontfamily{phv}\selectfont} % Helvetica-like (similar to Arial/Calibri)
\newcommand{\headerfontii}{\fontfamily{ptm}\selectfont} % Times-like (similar to Times New Roman)
\newcommand{\headerfontiii}{\fontfamily{ppl}\selectfont} % Palatino (elegant serif)
\newcommand{\headerfontiv}{\fontfamily{pbk}\selectfont} % Bookman (readable serif)
\newcommand{\headerfontv}{\fontfamily{pag}\selectfont} % Avant Garde-like (similar to Trebuchet MS)
\newcommand{\headerfontvi}{\fontfamily{cmss}\selectfont} % Computer Modern Sans Serif
\newcommand{\headerfontvii}{\fontfamily{qhv}\selectfont} % Quasi-Helvetica (another Arial/Calibri alternative)
\newcommand{\headerfontviii}{\fontfamily{qpl}\selectfont} % Quasi-Palatino (another elegant serif option)
\newcommand{\headerfontix}{\fontfamily{qtm}\selectfont} % Quasi-Times (another Times New Roman alternative)
\newcommand{\headerfontx}{\fontfamily{bch}\selectfont} % Charter (clean serif font)

% Custom Commands
\newcommand{\chinese}[1]{\begin{CJK}{UTF8}{gbsn}#1\end{CJK}} % Normal Chinese Font
\newcommand{\chinesebf}[1]{{\renewcommand{\bfdefault}{bx}\begin{CJK}{UTF8}{gbsn}\textbf{#1}\end{CJK}}} % Bold Chinese
\renewcommand*{\bibfont}{\normalfont\small}

\title{My Amazing Document}
\author{John Doe}
\date{\today}  % Adds the current date

\begin{document}
	\headerfontiii
	
	% Header Start
	\begin{center}
		{\Huge\textbf{Radwan Al-Shawesh}}
	\end{center}
	\vspace{-6mm}
	
	\begin{center}
		\small{
			\href{mailto:radwan.al.shawesh@gmail.com}{radwan.al.shawesh@gmail.com} | 
			\href{https://radwancs.github.io/cv/}{radwancs.github.io/cv}
		}
	\end{center}
	\vspace{-6mm}
	
	\begin{center}
		\small{
			\socialicon{\faWhatsappSquare} \href{https://wa.me/967782989639}{+967 782 989 639} |
			\socialicon{\faWeixin} WeChat ID: radwanCS |
			\socialicon{\faGithub} \href{https://github.com/radwanCS}{radwanCS}
		}
	\end{center}
	\vspace{-6mm}
	
	\begin{center}
		\small{City of Sana'a, Yemen}
	\end{center}
	\vspace{-4mm}
	% Header End

	% Summary Start
	\section{\texorpdfstring{\textbf{Summary} \hspace*{\fill} 
    \textcolor{darkblue}{\scriptsize [\href{https://1drv.ms/f/c/0b66680558f854cf/EmMcNN-2rp5JkBqREvrLziABZw0qcxK9gYBRxxkRwz2g9A?e=Dd3Xgb}{\faGlobe}] = Click to verify documents}}{Summary}}

	\vspace{1mm}
	\small{
		A passionate computer science enthusiast with a strong foundation in mathematics, computer science, software engineering, and 
		artificial intelligence. Driven by curiosity and a strong passion for research, I am constantly exploring new ways to innovate 
		and push the boundaries of what technology can achieve. If you're looking for someone who gets excited about breakthroughs in computer science, 
		embracing new challenges, and turning coffee into code, then we’re on the same page!
	}
	\vspace{-2mm}
	% Summary End
	
	% Personal Info Start
	\section{\textbf{Personal Information}}
	\vspace{2mm}
	
	\footnotesize{
	\centering
	\begin{tabularx}{\textwidth}{X@{\hskip 10pt}l@{\hskip 20pt}X@{\hskip 10pt}X}
		\textbf{Name}           & Redhwan Abdullah Thabit Al-Shawesh   & \textbf{Marital Status} & Married \\
		\textbf{Nationality}    & Yemeni                               & \textbf{Place of Birth} & Sana'a, Yemen \\
		\textbf{Gender}         & Male                                 & \textbf{Languages}      & Arabic, English, Chinese \\
		\textbf{Date of Birth}  & 12 October 1992                      & \textbf{Profession}     & Lecturer \\
	\end{tabularx}
	}
	\vspace{-4mm}
	% Personal Info End

	% Education Start
	\section{\textbf{Education}}
	\vspace{-0.4mm}
	\resumeSubHeadingListStart
	\resumeSubheading
	{East China Normal University [\href{https://1drv.ms/b/c/0b66680558f854cf/EYZd7X4rydJGoKDW_EY6kOIBcWqTedFBL9BoEi_vQ8Ndgw?e=dwkqIQ}{\faIcon{globe}}]}{Shanghai, China}
	{\textbf{M.S.E} Software Engineering}{Sep. 2018 - July 2021}
	\resumeItemListStart
	\item \textbf{Specialization:} Artificial Intelligence, Deep learning, Medical Big Data, and Computer Vision.
	\item \textbf{MSc Thesis:} Histopathological Colorectal Cancer Image Classification based on Convolutional Neural Network
	\item \textbf{Supervisor:} Prof. Chen YiXiang
	\item \textbf{GPA:} 4.21/5.00
	\item \textbf{Awards:} Shanghai Goverment Scholarship Type A
	\item \textbf{Relevant Coursework:} Computer Architecture, Algorithm Design and Complexity Analysis, Fundamentals of Artificial Intelligence, Data Visualization, Theoretical Foundation of Software, Software/Hardware Co-Design, Machine learning, Large-Scale Nonlinear Programming, Advanced Design Methodologies for Smart Systems, Seminar on Embedded Systems.
	\resumeItemListEnd
	
	\resumeSubheading
	{South East University [\href{https://1drv.ms/b/c/0b66680558f854cf/EZ6IBz28Vu1HkfYbkDgmtUUBh_bQMBNlrJH0y5fedP4pCg?e=dXOP9c}{\faIcon{globe}}]}{Nanjing, China}
	{\textbf{MTCSOL} Master of Teaching Chinese to Speakers of Other Languages }{Sep. 2016 - July 2018}
	\resumeItemListStart
	\item \textbf{MSc Thesis:} An Experimental Analysis of Pronunciation Errors in Chinese Initial Consonants by Yemeni Students
	\item \textbf{Supervisor:} Prof. Zhang TianLai
	\item \textbf{GPA:} 4.50/5.00
	\item \textbf{Awards:} CSC Scholarship Type A
	\resumeItemListEnd

	\resumeSubheading
	{Nanjing University of Aeronautics \& Astronautics [\href{https://1drv.ms/b/c/0b66680558f854cf/EWNwcEpNXSxDgGY2XtRoH8ABN-HndmwzFW5RBjuSeB4H-A?e=4fZaLe}{\faIcon{globe}}]}{Nanjing, China}
	{\textbf{B.Eng} Aeronautical Engineering}{Sep. 2012 - July 2016}
	\resumeItemListStart
	\item \textbf{Specialization:} Aircraft Control and Information Engineering
	\item \textbf{GPA:} 3.10/5.00
	\item \textbf{Awards:} CSC Scholarship Type A, Top 100 Outstanding Young Students
	\item \textbf{Relevant Coursework:} Linear Algebra, Algebra \& Trigonometry, Introduction to Computer Science, Computer Programming, Calculus 1,2 \& 3, Electrical Engineering \& Electronic Technique 1 \& 2, Physics 1 \& 2, Information Retrieval \& Utilization, Numerical Analysis, Discreet Mathmatics, Mathematical Equations, Software Engineering.
	\resumeItemListEnd
	
	\resumeSubheading
	{Tongji University [\href{https://1drv.ms/b/c/0b66680558f854cf/EYA7wC5Ad_FPjbqRLHAKbsUBUG4ZOGk8byilERusmPVQaQ?e=0xjWBs}{\faIcon{globe}}]}{Shanghai, China}
	{Preparatory Certificate in Science and Engineering}{Sep. 2011 - July 2012}
	\resumeItemListStart
	\item \textbf{Supervisor:} Prof. Li Ting
	\item \textbf{GPA:} 4.8/5.0
	\item \textbf{Awards:} CSC Scholarship Type A, Outstanding Academic Achievement Award, Excellent Attendance Award, and Active Participation in Various Activities Award.
	\item \textbf{Relevant Coursework:} Computer Science, Mathmatics, Physics, Scientific Chinese, Chemistry.
	\resumeItemListEnd
	
	\resumeSubHeadingListEnd
	\vspace{-6mm}
	% Education Ends

	% Research Interests Starts
	\section{\textbf{Research Interests}}
	\vspace{2mm} % Adjust spacing for clarity

	\begingroup
	\footnotesize{
	% Set the table layout for two-column alignment
	\renewcommand{\arraystretch}{1.4} % Adjusts row height for readability
	\setlength{\tabcolsep}{10pt} % Adjusts horizontal spacing between columns

	\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}X >{\raggedright\arraybackslash}X}
	\textbullet\ Machine Learning and Deep Learning & \textbullet\ Computer Vision \\
	\textbullet\ Natural Language Processing (NLP) & \textbullet\ Reinforcement Learning (RL) \\
	\textbullet\ AI Applications in Healthcare & \textbullet\ Autonomous Systems\\
	\textbullet\ Computer Architecture and Software System Design & \textbullet\ Algorithms and Computer Science Theory\\
	\end{tabularx}
	}
	\endgroup
	\vspace{-2mm} % Add spacing for section balance
	% Research Interests Ends

	% Research Experience Start
	\section{\textbf{Research Experience}}
	\vspace{-0.4mm}
	\resumeSubHeadingListStart
	
	\resumeProject
	{Enhancing Histopathological CRC Image Classification by using CNN}
	{Tools: [Python, TensorFlow, Keras, ResNet-50, Transfer Learning, Fine-Tuning, Macenko Method]}
	{Sep. 2020 - March 2021}
	{{}[\href{https://github.com/radwanCS/ResNet_50_enhanced_for_CRC_image_classification}{\textcolor{darkblue}{\faGlobe}}]}
	\resumeItemListStart
	\item \textbf{Institution:} East China Normal University.
	\item \textbf{Objective:} Investigated convolutional neural network (CNN) techniques for improving colorectal cancer (CRC) histopathological image classification.
	\item \textbf{Methods:} Adapted the ResNet-50 architecture using transfer learning and fine-tuning techniques. Leveraged pretraining on the ImageNet dataset, froze parameters in early layers, and retrained the dense and final layers to optimize feature extraction from CRC histopathological images in the NCT dataset.
    \item \textbf{Outcomes:} Achieved a \textbf{97.7\%} validation accuracy, demonstrating the model's potential for clinical applications in cancer diagnostics.
	\resumeItemListEnd
	
	\resumeSubHeadingListEnd
	\vspace{-6mm}
	% Research Experience End

	% Teaching Experience Starts
	\section{\textbf{Teaching Experience}}
	\vspace{2mm} % Increased space for better clarity
	
	\footnotesize{
	\textbullet\ {\normalsize{\textbf{Courses I have taught:}}}\\
	\vspace{2mm} % Increased space for better readability

	Teaching experience includes \textbf{1 year} at the University of Science \& Technology \textbf{(UST)}.

	\vspace{2mm} % Increased space for better readability
	\renewcommand{\arraystretch}{1.5} % Adjusts row height for readability
	\setlength{\tabcolsep}{12pt} % Increased horizontal space for clarity
	\rowcolors{2}{gray!10}{white} % Alternate row colors (2nd row gray, others white)
	\begin{tabularx}{\textwidth}{|X|c|c|c|}
		\hline
		\rowcolor[HTML]{CCCCCC} % Gray background for header
		\textbf{Course Title} & \textbf{Program} & \textbf{Semesters Taught} & \textbf{Mod of Teaching} \\
		\hline
		Computer Fundamentals & BSc & 1 & Lectures \& Lab\\
		\hline
		Introduction to Computer Science & BSc & 1 & Lectures \& Lab\\
		\hline
		Software Engineering & BSc & 1 & Lecturers \& Lab\\
		\hline
	\end{tabularx}
	
	\vspace{4mm} % Increased space after table for balance
	
	\textbullet\ {\normalsize{\textbf{Courses I am qualified and prepared to teach:}}}\\
	\vspace{2mm} % Increased space for better readability

	\renewcommand{\arraystretch}{1.5} % Adjust row height for better readability
	\setlength{\tabcolsep}{12pt} % Adjust column spacing
	\rowcolors{2}{gray!10}{white} % Alternate row colors (2nd row gray, others white)
	\begin{tabularx}{\textwidth}{|X|}
		\hline
		\rowcolor[HTML]{CCCCCC} % Gray background for header
		\textbf{Course Title} \\
		\hline
		Calculus\\
		\hline
		Computer Programming (C/C++, Java, Python)\\
		\hline
		Data Structures\\
		\hline
		Discrete Mathematics\\
		\hline
		Introduction to Information Science \& Technology\\
		\hline
		Object-Oriented Programming\\
		\hline
	\end{tabularx}

	\vspace{2mm} % Consistent space before closing section
	}
	% Teaching Experience Ends

	% Projects Section Starts
	\section{\textbf{Projects}}
	\vspace{-0.4mm}
	\resumeSubHeadingListStart

	\resumeProject
    {AI Pathologist: [Image Classification Python Applicaion for Lab Doctors]}
    {Tools: [Python, Qt for Python]}
    {March 2021 - April 2021}
	{{}[\href{https://github.com/radwanCS/ResNet_50_enhanced_for_CRC_image_classification}{\textcolor{darkblue}{\faGithub}}]}
    \resumeItemListStart
        \item Developed a software program to utilize my own CNN network.
        \item Designed the software to operate efficiently on both CPU and GPU, without requiring high-end hardware or third-party software dependencies.
        \item Optimized the user interface for simplicity, allowing pathologists and lab doctors to upload, classify, and analyze images efficiently.
    \resumeItemListEnd

	\resumeProject
	{Computer Science \& Technology Self Study Platform}
	{Tools: [Python, Sphinx, GitHub Pages, reStructuredText, Git, GitHub Actions(CI/CD)]}
	{May 2021 - Present}
	{{}[\href{https://radwancs.github.io/Tsinghua-CS-SelfStudy/index.html}{\textcolor{darkblue}{\faGithub}}]}
	\resumeItemListStart
	\item Developed a comprehensive self-study guide for Computer Science based on curricula from renowned universities like Tsinghua, MIT, and Harvard.
	\item Utilized Sphinx and reStructuredText to generate clean, readable documentation, deployed to GitHub Pages using Continuous Deployment with GitHub Actions.
	\item Created a structured learning roadmap, including suggested books, online resources, courses, and exams, designed to guide learners through the essential topics in computer science.
	\item Integrated practical resources like the REKCARC-TSC-UHT open-source project on GitHub to enrich the guide with real-world examples and tools.
	\resumeItemListEnd

	\resumeProject
	{Data Structure Visualization using Graphviz}
	{Tools: [C, Graphviz]}
	{Sep. 2022 - Present}
	{{}[\href{https://github.com/radwanCS/Data-Structure-Visualization-with-Graphviz}{\textcolor{darkblue}{\faGithub}}]}
	\resumeItemListStart
	\item Developed a tool for visualizing data structures like Binary Search Trees (BST) and Threaded Binary Trees using the Graphviz library.
	\item Provided interactive visualization for tree structures and operations, helping users understand internal relationships.
	\item Included future support for AVL Trees and Red-Black Trees for extended functionality.
	\resumeItemListEnd

	\resumeProject
	{The Oden Project}
	{Tools: [HTML, CSS, JavaScript, React, Node.js]}
	{April 2020 - May 2021}
	{{}[\href{https://github.com/radwanCS?tab=repositories}{\textcolor{darkblue}{\faGithub}}]}
	\resumeItemListStart
	\item Gained hands-on experience in front-end and back-end development, utilizing tools such as React and Node.js.
	\item Developed practical solutions for various common applications, applying modern development practices.
	\item Completed multiple projects as part of the Oden project process, including: \textbf{Social media site clone, Tic-Tac-Toe Game, Drawing App, Calculator App, Responsive Login Page, Admin Dashboard and Library App}

	\resumeItemListEnd

\resumeSubHeadingListEnd

	% Projects Section Ends

	% Publication Section start
	\section{\textbf{Patents and Publications}}
	\vspace{1mm}
		\nocite{*}  % This will include all entries from the .bib file even if not cited in the text
		% Filter by type
		\subsection*{Online}
		\printbibliography[type=online, heading=none]

		\subsection*{Thesis}
		\printbibliography[type=thesis, heading=none]
	% Publication Section Ends

	% Honors and Awards Starts
	\section{\textbf{Honors and Awards}}
	\vspace{-0.4mm}
	\resumeSubHeadingListStart
		
	\resumeProject
	{Shanghai Goverment Scholarship Type A}
	{East China Normal University}
	{Sep. 2018}
	{{}[\href{https://www.study-shanghai.cn/c.asp?action=AS_SS_Entry}{\textcolor{darkblue}{\faIcon{globe}}}]}
	\resumeItemListStart
		\item Awarded this scholarship to pursue a Master’s degree in Software Engineering.
		\item Successfully completed a three year master degree at ECNU.
	\resumeItemListEnd
	
	\resumeProject
		{China Goverment Scholarship Type A}
		{Embassy of China in Yemen}
		{Sep. 2011}
		{{}[\href{https://www.csc.edu.cn/studyinchina/}{\textcolor{darkblue}{\faIcon{globe}}}]}
	\resumeItemListStart
		\item Awarded this scholarship to pursue a bachelor degree.
		\item Successfully completed a one-year preparatory course at Tongji University.
		\item Successfully completed a four-year bachelor's degree at NUAA.
	\resumeItemListEnd
		
	\resumeProject
		{China Goverment Scholarship Type A}
		{Embassy of China in Yemen}
		{Sep. 2016}
		{{}[\href{https://www.csc.edu.cn/studyinchina/}{\textcolor{darkblue}{\faIcon{globe}}}]}
	\resumeItemListStart
		\item Awarded this scholarship to pursue a Master's degree in Chinese Language.
		\item Successfully completed a three-year master degree at SEU.
	\resumeItemListEnd
	
	\resumeProject
		{Top 100 Students Award}
		{Nanjing University of Aeronautical \& Astronautical Engineering}
		{Sep. 2015}
		{{}[\href{https://1drv.ms/b/c/0b66680558f854cf/EZs7uU2FlwhBtqCXhEjKeBwBNxDvedaqIt2Cz2pGCuhbpQ?e=u5CROZ}{\textcolor{darkblue}{\faIcon{globe}}}]}
	\resumeItemListStart
		\item This award was given for excellence in academic performance, recognizing me as one of the top 100 students in the university during the 2015-2016 academic year.
	\resumeItemListEnd
	
	\resumeProject
		{Certificate of Honor}
		{Tongji University}
		{June 2012}
		{{}[\href{https://1drv.ms/b/c/0b66680558f854cf/EdAygWujlQVKuntlVSHtJRIBFWMyYy7UMJXhswPmx3oSWQ?e=Y1Aupf}{\textcolor{darkblue}{\faIcon{globe}}}]}
	\resumeItemListStart
		\item Won the Outstanding Academic Achievement Award, Excellent Attendance Award, and Active Participation in Various Activities Award.
	\resumeItemListEnd
	
	\resumeSubHeadingListEnd
	\vspace{-6mm}
	% Honors and Awards End

	\begin{comment}
	\section{\textbf{Leadership Experience}}
	\vspace{-0.4mm}
	\resumeSubHeadingListStart
	\resumeProject
	{Leadership Role A}
	{Organization/Institution Name}
	{Month Year - Month Year}
	{{}[\href{https://organization-a-link.com}{\textcolor{darkblue}{\faIcon{globe}}}]}
	\resumeItemListStart
	\item Key responsibility or achievement in this role
	\item Quantifiable impact or improvement made during tenure
	\item Initiative taken or project led
	\resumeItemListEnd
	
	\resumeProject
	{Leadership Role B}
	{Organization/Institution Name}
	{Month Year - Month Year}
	{{}[\href{https://organization-b-link.com}{\textcolor{darkblue}{\faIcon{globe}}}]}
	\resumeItemListStart
	\item Key responsibility or achievement in this role
	\item Quantifiable impact or improvement made during tenure
	\item Initiative taken or project led
	\resumeItemListEnd
	
	\resumeSubHeadingListEnd
	\vspace{-6mm}
	\end{comment}

	% Experience Starts
	\section{\textbf{Employment History}}
	\vspace{2mm}

	\resumeSubHeadingListStart

	\subsection*{\underline{Full-Time Work}}
	\vspace{-1mm}

	\resumeSubheading
	{Foshan Safe Freight CO.,LTD | Safe CareMed [\href{https://www.safecaremd.com/}{\faIcon{globe}}]}{Foshan, China}
	{Software Engineer}{July 2021 - June 2023}
	\resumeItemListStart
	\item Customized and developed full ERPNext modules using Python and Frappe Bench, optimizing internal workflows and automating key business processes, boosting workflow efficiency by 50\%.
	\item Maintained Linux servers with 99.9\% uptime and strengthened security.
	\item Built responsive UIs with JavaScript, jQuery, HTML, and Bootstrap 5, improving usability by 25\%.
	\item Developed and managed multiple WordPress sites, creating custom themes and plugins to enhance functionality and improve SEO ranking.
	\item Collaborated with the marketing team to enhance visibility, refine strategies, and actively contributed to social media marketing efforts.
	\item Designed visuals and video edits using Photoshop, Illustrator, and Adobe Premiere for websites, applications, and social media campaigns, enhancing brand visibility and user engagement.
	\resumeItemListEnd
	
	\vspace{-3mm}
	\subsection*{\underline{Part-Time Work}}
	\vspace{-3mm}

	\resumeSubheading
	{{University of Science \& Technology [\href{https://ust.edu.ye/cit/}{\faIcon{globe}}]}}{Sana'a, Yemen}
	{Lecturer}{June 2024 - Present}
	\resumeItemListStart
    \item Developed and delivered engaging lectures in \emph{Software Engineering, Data Structures \& Algorithms, Introduction to computer science, and Computer Orginization} enhancing student understanding and performance.
	\resumeItemListEnd
	\vspace{-3mm}
	\resumeSubHeadingListEnd
	% Experience Ends

	\section{\textbf{Volunteer Experience}}
	\vspace{-0.4mm}
	\resumeSubHeadingListStart

	\resumeProject
	{Volunteer Teaching}
	{Gansu Province - Baiying city - Hepan Junior High School}
	{June 2015 - July 2015}
	{{}[\href{https://1drv.ms/b/c/0b66680558f854cf/EWhZisbqvTNClGJQgjoSEg8BX4o5KTUrmbUno6iK2k-XtA?e=4Ugpkl}{\textcolor{darkblue}{\faIcon{globe}}}]}
	\resumeItemListStart
	\item Taught science in English to junior high school students during a 15-day volunteer teaching and cultural exchange program.
	\item Promoted cross-cultural understanding and improved students' English communication skills through interactive science lessons.
	\item Recognized as an NUAA Advanced Individual of Summer Social Practice for contributions to education and community development.
	\resumeItemListEnd
	
	\resumeSubHeadingListEnd
	\vspace{-6mm}
	
	\begin{comment}
	\section{\textbf{Professional Memberships}}
	\vspace{-0.4mm}
	\resumeSubHeadingListStart
	\resumePOR{Professional Organization A}
	{, Membership ID: XXXXXXXX}
	{Month Year - Present}
	\resumePOR{Professional Organization B}
	{, \href{https://membership-certificate-link.com}{Membership ID: XXXXXXXX}}
	{Month Year - Present}
	\resumePOR{Professional Organization C}
	{, \href{https://membership-certificate-link.com}{Membership ID: XXXXXXXX}}
	{Month Year - Present}
	
	\resumeSubHeadingListEnd
	\vspace{-6mm}
	
	\section{\textbf{Certifications}}
	\vspace{-0.2mm}
	\resumeSubHeadingListStart
	\resumePOR{}{\href{https://certification-link-a.com}{
			\textbf{Certification A}
	}}{Month Year}
	\resumePOR{}{
		\textbf{Certifying Body:} {{\href{https://certification-link-b.com}{Certification B}}}}{Month Year}
	\resumePOR{}{
		\textbf{Certifying Body:} {{\href{https://certification-link-c.com}{Certification C}}}}{Month Year}
	\resumePOR{}{\href{https://certification-link-d.com}{
			\textbf{Certification D}
	}}{Month Year}
	
	\resumeSubHeadingListEnd
	\vspace{-6mm}
	\end{comment}

	% Skills Starts
	\section{\textbf{Skills}}
	\vspace{1mm}
	\resumeHeadingSkillStart
	\resumeSubItem{Programming Languages:}
	{C/C++, Python, Java, SQL}
	\resumeSubItem{Data Science \& Machine Learning:}
	{Pandas, NumPy, Scikit-learn, TensorFlow, Keras, Matplotlib, Seaborn}
	\resumeSubItem{Operating Systems:}
	{Linux(Debian, Ubuntu, Fedora), Windows}
	\resumeSubItem{Database Systems:}
	{MySQL, PostgreSQL, MongoDB, SQLite}
	\resumeSubItem{DevOps \& Version Control:}
	{Git, GitHub, CI/CD}
	\resumeSubItem{Web Technologies:}
	{HTML, CSS, Bootstrap, JavaScript, React, Node.js}
	\resumeSubItem{Mathematical \& Statistical Tools:}
	{MATLAB}
	\resumeSubItem{Software Engineering:}
	{UML, Object-Oriented Design (OOD), Software Architecture, Design Patterns, Software Development Lifecycle (SDLC)}
	\resumeSubItem{Teaching Skills:}
	{Curriculum Design, Classroom Management, Assessment \& Evaluation, Student Mentoring, Lecture Preparation}
	\resumeSubItem{Research Skills:}
	{Experimental Design, Data Analysis, Scientific Writing, Literature Review, Research Methodologies, Grant Writing}
	\resumeSubItem{Other Tools \& Technologies:}
	{LaTeX, Jupyter Notebooks, Microsoft Office, Photoshop, Illustrator, Premiere}
	\resumeHeadingSkillEnd
	% Skills Ends

	% Additional Info Start
	\section{\textbf{Additional Information}}
	\vspace{1mm}

	\small{
    \textbf{Languages:} 
    \begin{itemize}[leftmargin=*]
        \item \textbf{Arabic:} Native speaker.
		\item \textbf{English:} Fluent in reading, writing, and listening, with average speaking skills. Completed a bachelor's program taught in English and published academic papers in English. My primary, middle, and high school education was primarily in English.
		\item \textbf{Chinese:} Passed HSK Level 6, the highest language proficiency certification in Chinese.
    \end{itemize}
	\vspace{-4mm}
	% Additional Info End
	
	\section{\textbf{References}}
	\vspace{-0.2mm}
	\small{
		\begin{enumerate}[leftmargin=*,labelsep=2mm]

			\item \textbf{Professor Chen YiXiang (\chinesebf{陈仪香}) [\href{https://1drv.ms/b/c/0b66680558f854cf/EbFpHDKA10FGiAizXAOuDJYBzRX9TGkOwxiMgaOED5dEIg?e=70cLSA}{\faIcon{globe}}]}\\
			Professor, College of Software Engineering\\
			East China Normal University\\
			Email: yxchen@sei.ecnu.edu.cn\\
			Phone: +86-186-2181-5769\\
			\textit{Relationship: Master's Degree Academic Advisor}

			\item \textbf{Prof. (Dr) Wang Wei Ying [\href{https://1drv.ms/b/c/0b66680558f854cf/EbFH8uGW5ThBq6ndiB9DKYsBhIrjYMmULQglMyAETwtpag?e=UX86MS}{\faIcon{globe}}]}\\
			Professor, Department of Engineering\\
			Nanjing University of Aeronautical \& Astronautical Engineering\\
			Email: meewywang@nuaa.edu.cn\\
			Phone: +86-138-5151-4220\\
			\textit{Relationship: Head Supervisor during a Design Project}
			
			\item \textbf{Prof. (Dr) Qian Yan (\chinesebf{钱焱}) [\href{https://1drv.ms/b/c/0b66680558f854cf/Eam0QZt12EVDuapdewUNDsEBnJfOx8l1ClQttWsvVWATNA?e=PW8Ogm}{\faIcon{globe}}]}\\
			Professor, Department of Business Administration\\
			Nanjing University of Aeronautical \& Astronautical Engineering\\
			Phone: +86-25-8489-6220\\
			\textit{Relationship: Instructor}
			
			\item \textbf{Dr. Li Ting (\chinesebf{李挺}) [\href{https://1drv.ms/b/c/0b66680558f854cf/Ee6VsE2GSOxNoGe7cg1dnhoBg1g6GVJuUYOy9DL94XeAVQ?e=dmdVsT}{\faIcon{globe}}]}\\
			Head Teacher, Department of International Cultural Exchange\\
			Tongji University\\
			Email: liting0811@126.com\\
			Phone: +86-138-1838-5961\\
			\textit{Relationship: Head teacher}
		\end{enumerate}
	}
	
\end{document}